My English activity log

### 2019-11-17 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 17/11/2019

>>>>

13/11/2019 : I watched a video about CRISPR https://www.youtube.com/watch?v=MnYppmstxIs.

15/11/2019 : I watched a video about ATP https://www.youtube.com/watch?v=23ZzI6WZS28.

16/11/2019 : I watched a video about bacteria https://www.youtube.com/watch?v=ORB866QSGv8.

17/11/2019 : I watched a video about autotrophs and heterotrophs https://www.youtube.com/watch?v=f8G7IulYxiA and I read the eighth of "The Hobbit".
